\documentclass{letter}
\usepackage[headheight=0pt,headsep=0pt]{geometry}
\signature{Jon Allen}
\address{P.O. Box 52 \\ Fargo, ND 58107}
\begin{document}
\begin{letter}{}
\opening{Dear Sir or Madam:}

In this letter I wish to give you an idea of who I am. This will I hope convince you that I would be a great asset for your organization. I will do so by telling you a bit of my story. It begins (as it does with most people) in my childhood.

When my parents brought home an Apple IIc computer I was immediately fascinated. Seeing my interest, my parents parents changed my life by obtaining a used Applesoft BASIC manual. It was incredible! By third grade I had figured out how to enable high resolution graphics and to write to disk (the manual only covered tape). I was also reaching the limits of what I could do with BASIC.

This is where I really began to learn how computers work. Soon I was an expert on the 65C02 microprocessor. I can remember sitting at school in the 6th grade, carefully writing down the machine code for games in a notebook, and drawing the sprites out on graph paper. As soon as I was home, I would eagerly enter the game I had so carefully crafted. Then I would happily spend my evenings debugging and sometimes even playing my creations.

Of course I didn't know it at the time, but all of this computer stuff was created by mathematicians initially. I soon found that as I progressed in school, I had already been taught all about algebra, fractions, vectors, and so on from my computer. This is probably why I always kind of liked math.

As I moved into high school I discovered that graphing calculaters were really just computers also. I built a cable that would allow me to hack on my Texas Instruments calculator, and soon I became quite an expert on it. When I was a senior in high school, I even received an award from Intel for a compiler I wrote.

A few years later, I found I wasn't really learning at the pace I liked (kids have so much more free time than adults) and so I went back to school. Of course computer science was a no brainer, or so I thought. This turned out to be kind of a mistake. There were some things to learn in the CS program. Unfortunately, given my background, those things were few and far between. I soon discovered that where I was really learning and having fun was with the calculus and linear algebra courses I was taking. Since I was young thought I knew everything, I dropped out.

For a while I was happy delivering pizzas and working on open source software, or taking random math courses at the local university in my free time. But all things must end. Fast forward a few years and I found myself with a family. So back to school, this time I made the right choice and finished with a degree in Mathematics.

Now I'm looking for two things, a stable day job that will support my family, and some interesting problems with computers that need solutions. I know that if you choose me to for your company you will be very surprised at how well you chose.
\closing{Thank you,}
%\ps{P.S. Here goes your ps.}
%\encl{Enclosures.}
\end{letter}
\end{document}
